### 2019-04-01 paper-template.Rmd
@Fsolt original template.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "An Example Article" 
thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](http://github.com/fsolt/example_article). Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu). Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Ahmad S. Qabazard
  affiliation: University of Iowa
abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
keywords: "these, always seem silly, to me, given google, but regardless"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: single
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load all the packages you will use below 
library(dotwhisker)
library(tidyverse)
```

# Introduction to RMarkdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r mtcars}
summary(mtcars)
```

---
# This is a comment, set off with --- and started with #.  Comments are good for notes to self that you don't want to show up in the output.  Below is LaTeX code for a page break.
---
\pagebreak 
## Including Plots

You can also embed plots, for example:

```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:dotwhisker_plot}Dot-and-Whisker Plot Example"}
m1 <- lm(mpg ~ wt + cyl + disp + gear, data = mtcars)
m2 <- update(m1, . ~ . + hp) # add another predictor
m3 <- update(m2, . ~ . + am) # and another 
dwplot(list(m1, m2, m3),
       vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% # plot line at zero _behind_ coefs
    relabel_predictors(c(wt = "Weight",                       
                         cyl = "Cylinders", 
                         disp = "Displacement", 
                         hp = "Horsepower", 
                         gear = "Gears", 
                         am = "Manual")) +
     theme_bw() + xlab("Coefficient Estimate") + ylab("") +
     geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
     ggtitle("Predicting Gas Mileage") +
     theme(plot.title = element_text(face="bold"),
           legend.position = c(0.007, 0.01),
           legend.justification = c(0, 0), 
           legend.background = element_rect(colour="grey80"),
           legend.title = element_blank()) 
```

Figure \ref{fig:dotwhisker_plot} is a plot made using the \texttt{dotwhisker} package [@Solt2015c]. Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Citations
Want to cite something?

1. Find your cite key in your bib file.
1. Put an @ before it, like @Solt2017, or whatever it is
1. @Solt2017 creates an in-text citation
1. [@Herndon2014] creates a parenthetical citation

As @Gelman2014 note, the garden of forking paths can pose problems for researchers even when they are acting in good faith.

#Zotero

## Other Common Things

> This will create a block quote, if you want one.
Dropping a footnote is easy.^[See? Not hard at all.]

### 2019-04-02 paper-template.Rmd
Text

@@
     template: svm-latex-ms2.tex
-title: "An Example Article" 
-thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](http://github.com/fsolt/example_article).
-Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).
+title: "Information, Ideology, and Anti-Vaccination Attitudes" 
+thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](https://github.com/aq92/7450paper.git).
+Corresponding author: [ahmad-qbazard@uiowa.edu](mailto:ahmad-qabazard@uiowa.edu).
 Current version: `r format(Sys.time(), '%B %d, %Y')`."
@@
   affiliation: University of Iowa
-abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
-keywords: "these, always seem silly, to me, given google, but regardless"
+abstract: "Anti-vaccination attitudes are prevalent among individuals affiliated with both major political parties.
+What determines anti-vaccination attitudes?
+Using survey responses of 1,000 US adults, I find that individual and state level variables contribute to attitudes towards vaccination.
+Using data from a 2015 telephone survey, I identify anti-vaccination attitudes using item response models.
+I show the presence of anti-vaccination attitudes among respondents by looking at responses to survey questions using graded response and nominal response models.
+I find that respondents from states with higher insured citizens are less likely to have skeptical attitudes towards vaccinations.
+I established the necessity of looking at vaccinations as latent constructs by showing the difference in model predictions.
+Using a mixed linear model, I predict values of a latent construct, theta, and the results show relationships that are obscured by looking at direct responses with a multinomial logit."
+keywords: "Vaccination, State Politics"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
-fontsize: 11pt
+fontsize: 12pt
 spacing: single
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-# load all the packages you will use below 
-library(dotwhisker)
-library(tidyverse)
-```
+####Introduction:
 
-# Introduction to RMarkdown
+Resistance to vaccination has existed since vaccination regimens were first administered.
+During the last several years, opposition to vaccination has been motivated by perceived links to autism.
+Although links between vaccinations and autism have been refuted, citizens are still concerned.
+I argue that there are three reasons that should motivate political scientists to explore anti-vaccination sentiments.
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+First, prominent political figures voiced concerns about links between vaccinations and autism.
+President Trump, along with Republican candidates Ben Carson and Rand Paul, claimed the current vaccination regimens are linked to autism in the Republican Presidential Debate.
+Concerns about vaccinations are also voiced by Democratic politicians.
+Dennis Kucinich, a former US congressman and gubernatorial candidate, argued that parents should determine if their children should get vaccinated.
+Since voters look to politicians for informational shortcuts, anti-vaccination sentiments have political consequences (Lupia 1994, Lau & Redlawsk 2001).
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+Second, interest groups defending vaccine freedom have become more prominent.
+Vaccine freedom groups are active in both Republican and Democratic stronghold states.
+For example, the Michigan Vaccine Freedom Political Action Committee has endorsed candidates on all major ballots during the 2018 midterm elections.
+Interestingly, Michigan Vaccine Freedom PAC endorsed Republicans, Democrats, and Independents.
+Scholars have posited that interest groups can influence the political agenda (Baumgartner & Jones 1991).
+The fact that interest groups are advocating policy premised on skepticism towards vaccinations should drive scholars to explore anti-vaccination sentiments.
 
-```{r mtcars}
-summary(mtcars)
-```
+Third, citizens that vote in democracies should be informed.
+We know that levels of political knowledge are concerning in the United States (Delli Carpini and Keeter 1996).
+However, information that leads to concerns about vaccination is not necessarily linked to voter ignorance.
+While there has been media coverage that refutes links between vaccinations and autism, misconceptions persist.
+Perhaps evidence of Nyhan and Reifler (2010)’s failure of corrections, media coverage of vaccinations has not eased concern even after measles and mumps outbreaks.
+Therefore, scholars should explore variations that lead to increased skepticism toward vaccinations.
 
----
-# This is a comment, set off with --- and started with #.  Comments are good for notes to self that you don't want to show up in the output.  Below is LaTeX code for a page break.
----
-\pagebreak 
-## Including Plots
+This article departs from the third motivation for exploring anti-vaccination sentiments.
+Using a survey of 1000 adults in 50 states, I examine responses to a series of questions that capture anti-vaccination attitudes.
+First, I proceed to show the existence of anti-vaccination attitudes as a latent construct.
+I use both graded and nominal response models to show the presence of the latent construct.
+Then, I incorporate covariates that predict responses to direct questions on concerns about vaccinations.
+I use a multinomial logit model to predict the probability of particular responses.
+Finally, I show that individual and state-level covariates predict the parameter of anti-vaccination attitudes.
+Here, I use a mixed linear model with random coefficients and link the model to the theta parameter in the item response model.
 
-You can also embed plots, for example:
+####Informational, Ideological, and Recent Perspectives on Anti-Vaccination Attitudes:
 
-```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:dotwhisker_plot}Dot-and-Whisker Plot Example"}
-m1 <- lm(mpg ~ wt + cyl + disp + gear, data = mtcars)
-m2 <- update(m1, . ~ . + hp) # add another predictor
-m3 <- update(m2, . ~ . + am) # and another 
-dwplot(list(m1, m2, m3),
-       vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% # plot line at zero _behind_ coefs
-    relabel_predictors(c(wt = "Weight",                       
-                         cyl = "Cylinders", 
-                         disp = "Displacement", 
-                         hp = "Horsepower", 
-                         gear = "Gears", 
-                         am = "Manual")) +
-     theme_bw() + xlab("Coefficient Estimate") + ylab("") +
-     geom_vline(xintercept = 0, colour = "grey60", linetype = 2) +
-     ggtitle("Predicting Gas Mileage") +
-     theme(plot.title = element_text(face="bold"),
-           legend.position = c(0.007, 0.01),
-           legend.justification = c(0, 0), 
-           legend.background = element_rect(colour="grey80"),
-           legend.title = element_blank()) 
-```
+Concerns about vaccination have been studied extensively by scholars in public health and behavioral sciences.
+Much of the literature focuses on the sources of information reported by survey respondents.
+The works underscore the importance of background factors and sources of information in the Theory of Planned Behavior (TPB).
+The Theory of Planned behavior is a cognitive processing model that links attitudes to behavioral intentions.
+Attitudes are determined by knowledge, behavioral beliefs, and subjective norms.
+Kennedy et al.
+(2011) ask respondents whether they plan on having their children follow recommended vaccine regimens.
+Surveying 475 individuals, Kennedy et al.
+show that 93.4 percent of the respondents plan to follow recommended vaccination regimens.
+In their sample, 81.7 percent of the respondents listed their doctor as the most important source of information on vaccines.
+Wheeler and Buttenheim (2013) also focus on sources of information on vaccines.
+They find that non-physician sources of information play an important role in parents’ intention to follow alternative immunization regimens.
+Wheeler and Buttenheim argue that communication from physicians plays an important role in addressing vaccine concerns.
+Salmon et al.
+(2004) mail surveys to a sample of 1000 schools in Colorado.
+Salmon et al.
+find that children attending schools with a respondent that was a registered nurse were less likely to have vaccine exemptions than children attending school where the respondent was not a nurse.
 
-Figure \ref{fig:dotwhisker_plot} is a plot made using the \texttt{dotwhisker} package [@Solt2015c].
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+Another line of literature emphasizes ideology and argues against the “knowledge deficit” approach.
+Baumgaertner et al.
+(2018) show that ideology has direct effects on anti-vaccination attitudes.
+Baumgaertner et al.
+find that conservative respondents are less likely to hold pro-vaccination attitudes.
+In work that emphasizes the role of ideology, political ideology is defined as a set of beliefs that influences an individual’s perception of normative order in society (Douglas & Wildavsky 1982, Baumgaertner et al.
+2018).
+The literature on ideology also links ideology to cognitive decisions and evaluation of risk.
+Therefore, there is an expectation for ideology to influence attitudes towards vaccinations directly.
+
+####Testing the Knowledge Hypothesis with State Level Variation:
+
+I argue that there is an indirect relationship between health policy and anti-vaccination attitudes.
+More specifically, I predict that individuals from states that facilitate more interaction with medical professionals will be less likely to hold anti-vaccination attitudes.
+The relationship between health policy and attitudes is premised on knowledge deficit theory which explains anti-vaccination attitudes.
+Knowledge based theories emphasize interaction with medical professionals as reliable sources of information.
+States that have health policy that facilitates more interaction should be expected to have individuals that are less likely to be skeptical towards vaccines.
+While interaction with doctors is primarily determined by the behavior of individuals, state health care policy may be designed to facilitate more interaction with medical professionals.
+By state health care policy, I am referring to the determinants of health insurance enrollment.
+I use data from the Kaiser Family Institute to account for state level variation in citizen interaction with medical doctors and health insurance coverage.
+The data is merged with individual level data from the 2015 Pew Center Survey.
+
+When studying anti-vaccination attitudes, the primary concern is with the individuals.
+However, Salmon et al.
+(2004) show that variation at the group level, in their case the school level, leads to variation at the individual respondent level.
+Salmon et al.
+show that the presence of registered school nurses is associated with less rejection of physician recommended vaccine regimens.
+Available data allows for an assessment of the state-level background factors.
+Previous work has shown that information from medical professionals leads to less skepticism towards vaccines (Wheeler and Buttenheim 2013).
+I test whether factors lead to more access to medical professionals can be linked to anti-vaccination attitudes.
+I look at, both, the percent of individuals that had not seen doctors in over a year and the percent of uninsured individuals in a state.
+We may know the percent in the state that have not seen doctors.
+However, we can not be sure whether this is the case because of access to doctors or merely due to the behavior of an individual.
+Looking at the percent uninsured in a state reflects more policy variation.
+Therefore, I hypothesize that:
+
+- H1: Individuals from states with less interaction with medical professionals are more likely to hold anti-vaccination attitudes.
+
+- H2: Individuals from states with higher uninsured populations are more likely to have anti-vaccination attitudes.
+
+####Anti-Vaccination Attitudes in the Pew Center Survey:
+
+                     [Insert Table 1 here]
+
+I show that, in the 2015 Pew Center Survey, there is evidence of the existence of anti-vaccination attitudes.
+My work differs from previous work because I treat anti-vaccination attitudes as latent constructs, measuring them using item response theory.
+I argue that measuring attitudes as latent constructs is superior to previous approaches because it uses responses to a range of questions.
+I proceed by looking at a collection of questions relevant to vaccination and concerns about side effects.
+In addition to collecting the demographics of the survey participants, the survey asks five direct questions about vaccinations.
+First, the survey asks about the importance of vaccinations.
+Second, the survey asks how much information a respondent heard about the advantages of vaccinations.
+Third, respondents are asked about exposure to information about the disadvantages of vaccinations.
+Fourth, respondents are asked if the vaccinations are more dangerous than the diseases they are designed to prevent.
+Fifth, the survey asks respondents if they think certain vaccines cause autism.
+The responses are coded as ordinal ranging from, for example, “Not at all important” to “Extremely Important.”
+
+To establish a relationship between questions or to uncover a latent construct, I employ item response models because of the nature of the questions and responses.
+I do not use additive models because these models treat each question with equal weight.
+Moreover, additive models do not reflect measures of uncertainty (Warshaw 2018).
+I do not use factor analysis models because they are not well suited for dichotomous and ordinal responses (Kaplan 2004, Treier & Hillygus 2009).
+Item response models are the most appropriate models for ordinal and nominal responses (Johnson and Albert 2006).
+Given that models taken from item response theory are the most appropriate, I employ both a graded response model and a nominal response model.
+
+#####Categorical Item Response Models:
+
+To test for the existence of a latent construct from responses to the five major questions, I use a graded response model and a nominal response model.
+Both models calculate difficulty and discrimination parameters given responses to survey questions.
+The graded response model is an extension of a standard two parameter item response model.
+Graded response models are unique because they allow items to vary in their discriminations and difficulty parameters.
+The responses to the five questions are ordered.
+Assume the order is from 0 to k.
+The following equation illustrates how the model determines the probability of a particular response:
+
+$$Pr(Y_{ij} \ge k|\alpha_{i},\beta{i},\theta_{j})= \frac{exp(\alpha_{i}\theta_{j} - \beta_{ik})} {1 + exp(\alpha_{i}\theta_{j} - \beta_{ik})}$$
+
+where alpha is the discrimination parameter for a particular item.
+Beta represents the cut point k between each response.
+Theta is the latent trait for a particular person j.
+Graded response models calculate the probability of observing outcome k or ones greater.
+	In nominal response models, the same logic is extended to non-ordered categorical items.
+Nominal models also allow each item to vary in difficulty and parameter.
+The model, proposed by Bock (1972), is helpful because it allows the prediction of each particular response.
+The following equation illustrates the probability of an individual person j selecting a particular category k for each item i.
+
+$$Pr(Y_{ij}= k | \alpha_{i},\beta_{i},\theta) = \frac{exp(\alpha_{ik}\theta_{j}+\beta_{ik})} {\sum_{h=1}^{K} exp(\alpha_{ih}\theta_{j}+\beta_{ih})}$$
+
+#####Model Results and Interpretation:
+
+For the item response models, I drop the respondents that did not answer the questions in Table 1.
+After fitting both a graded response model and a nominal response model, I find that there is evidence for the existence of a meaningful latent trait for three questions.
+The three questions are: (1) How important is it for parents to vaccinate their children?
+(2) Do certain vaccines cause autism in children?
+(3) Do you think vaccines are more dangerous than the disease they are designed to prevent?
+The graded response model yields a non-zero discrimination parameter that is statistically significant for the three questions.
+The nominal response model reports statistically significant differences between responses that are skeptical and not skeptical of vaccines.
+For example, there is a statistically significant difference between the responses that vaccination is “Extremely Important” and “Not Very Important.” The results are included in Table 1 of the appendix.
+
+Beyond the models’ results, Jackman (2008) recommends discussing reliability and validity.
+Regarding reliability, the models report measures of uncertainty that are below conventional measures.
+I argue that the models measured “what they are supposed to be measuring.” Especially in the ordered, graded response model, the distinction between high and lower ordered responses captures a skepticism of vaccination.
+The importance of vaccination and perception of links with autism are both loaded questions that capture the attitudes of individuals towards vaccination.
+Therefore, I am not worried about multidimensionality.
+To test the unidimensionality assumption, I used factor analysis and found that, once accounting for the latent attitude, the questions yield one factor.
+
+                     [Insert Figure 1 & 2 here]
+
+Figures 1 and 2 are characteristic curves that show the role of theta in the probability of observing particular responses.
+Theta is the latent construct or attitude measure.
+For vaccine importance, Figure 1 shows that as theta increases the probability of responding “Extremely Important” decreases.
+When the “Extremely Important” line intersects with the red line, that value of theta yields a higher probability of responding “Very Important.” As theta increases respondents will be more likely to respond, “Somewhat Important.” Finally, a value of theta that continues to increase yields higher probability of responding “Not at all important.”
+
+The role of theta is professing itself more in Figure 2.
+Here, respondents are asked whether certain vaccines cause autism.
+As theta increases the probability of responding “No” decreases.
+As theta increases, we encounter less certain respondents that were “Unsure” if vaccines cause autism.
+When the green line intersects with the blue line, for values of theta greater than 2, respondents are more likely to respond “Yes.”
+
+Taken together, the figures illustrate that the models are measuring what is intended for them to measure.
+As theta increases, the more likely the respondents hold anti-vaccination attitudes.
+In the following section, I predict responses to each of the two questions.
+After looking at predictions of raw responses, I predict theta.
+
+####Multinomial Logit:
+
+In this section I discuss the results of models that directly predict responses.
+As opposed to looking at the theta parameter of the anti-vaccination attitude, I test how the covariates do in predicting raw responses.
+I use both individual and state level covariates in these models.
+After discussing the multinomial model presented, I discuss covariates in both models, and explain the results.
+I show that looking at the latent constructs is necessary because the covariates do not do well at predicting responses.
+
+To test individual level variables, I fit a multinomial logit model to predict individual responses.
+The multinomial model is clustered by state.
+The model tests both the importance of vaccinations and vaccinations and autism responses as the dependent variables.
+In this model, I incorporate state level variables.
+I use a multinomial model instead of an ordered logit.
+Ordered logit models do not allow clustering by state.
+
+#####Independent Variables:
+
+I argue that states that facilitate frequent interaction between citizens and doctors should have less skepticism towards vaccination.
+If citizens get their information from doctors, they should be more likely to have less professed anti-vaccination concerns.
+In order to capture the conditions that facilitate frequent interaction between individuals and doctors, I include several state-level variables.
+State level data is taken from the Kaiser Family Foundation dataset on health care.
+State level variables are from 2014, a year before the survey was conducted.
+The first state-level variable is percent of adults that have not seen a doctor in the past twelve months.
+The second variable is a measure of the percent of uninsured individuals by state.
+
+I also use individual level data that was collected during the survey.
+I use an ideology variable to test competing hypotheses about anti-vaccination sentiments.
+The ideology variable is an ordered variable that ranges from very conservative to very liberal.
+Baum (2011) argues that anti-vaccination opinions are shaped by ideology.
+Although Baum was looking at H1N1 vaccines, there is still reason to believe that the logic applies to the claims made in this article.
+
+#####Controls:
+
+At the individual level, I control for seven variables.
+I control for religiosity to account for variation explained by religious belief.
+States allow exemptions from vaccination for religious reasons.
+Therefore, religious concerns are expected to influence attitudes towards vaccinations.
+The religiosity variable is measured by church attendance.
+I include age to account for a generational differences between respondents.
+The variable is ordinal and is broken into ten year intervals.
+I include education to account for variation in knowledge that results from differences in formal education.
+The variable is ordinal and measures whether respondents completed high school, some college, college, or post graduate degrees.
+There is reason to believe that differences in income may allow more access to reliable information or alternate information.
+Income is measured as monthly household income.
+I include a dichotomous variable that indicates for whether the respondent was a parent.
+I include gender and race to account for demographic and other distinctions between respondents.
+A respondent is a male if the gender variable equals 1.
+Race is measured as a dichotomous variable and equals 1 when the respondent is white.
+
+At the state level I include a control that accounts for the percent of children that are uninsured.
+The control is necessary to separate the state policy implications.
+Children are insured under federal mandates.
+If they are not separate from the percent uninsured variable it would be will be misleading.
+I include an interaction between percent health insurance coverage and individual ideology.
+I include this variable because I use a multilevel modelling in Table 3.
+Therefore, it is included in both models so they are consistent.
+
+                     [Insert Table 2 here]
+
+#####Results:
+
+The results are presented in Table 2.
+The omitted response is the baseline category for each model.
+Model 1 uses the question about the importance of vaccinations as the dependent variable.
+Model 2 uses perception of links to autism as the dependent variable.
+Based on the results, there is no evidence for any of the variables having a consistent effect on vaccine skepticism.
+Consistency would require that variables predict a higher likelihood of finding vaccines not important and expressing worry about links to autism.
+In both models, particular variables may predict a response but not a consistent attitude.
+The results illustrate the limits of looking at direct responses and not using item response models.
+
+                     [Insert Table 3 here]
+
+####Item Response Models:
+
+More meaningful results are observed using item response models.
+In the previous model, I predicted responses to each question.
+Here, I will predict the value of theta, conditional on the covariates.
+I use a mixed linear model and group respondents according to states.
+The dependent variable is the predicted value of theta for each respondent.
+I find no statistically significant relationship between the percent of individuals that have seen doctors and anti-vaccination attitudes.
+I find, all else equal, that higher values of theta are associated with individuals from states with higher uninsured populations.
+Therefore, the results only confirm my second hypothesis.
+
+There seems to be a link between state health care policy and anti-vaccination attitudes.
+I predicted that the link operates through interaction with doctors.
+However, the variable that measures interaction with doctors is not statistically significant.
+Given the controls that are included at the individual-level the results still suggest that there is more evidence for the knowledge deficit theory than ideology.
+The results also indicate that, all else equal, more educated respondents have lower skepticism towards vaccination.
+Also, white respondents are more likely to have higher skepticism.
+Men are less likely to have skepticism towards vaccination.
+However, these results are not theorized in this article.
+
+####Conclusion:
+
+Although anti-vaccination sentiments receive coverage in the news, social scientist have not studied them extensively.
+The medical community agrees that there is no evidence that links childhood vaccination regimens to autism.
+However, politicians and interest groups act based on misconception.
+In this article, I show that anti-vaccinations sentiments are more prevalent in states where individuals have less interaction with medical professionals.
+
+I argue against claims that attribute anti-vaccination sentiments to ideology.
+Beyond the fact that politicians on both sides of the ideological spectrum have raised these concerns, I show that there is no evidence of effects of ideology in the 2015 survey.
+I argue in favor of the knowledge deficit hypothesis.
+My findings expand on work that finds that more reliable sources of information lead to less skepticism towards vaccination.
+
+Future research should begin by gathering more data on anti-vaccination sentiments.
+With individual-level data on interaction with doctors, I could have more evidence to test the link between health policy and anti-vaccination attitudes.
+Also, the effects of measles and mumps outbreaks on public opinion is not clear.
+With more data across different points in time, scholars may be able to identify the effects outbreaks as information shocks.
+
+******
+
+####Tables and Figures
+
+![Descriptive](Table1.png)
+
+![Item Charateristic Curve p918](Figure1.png)
+![Item Charateristic Curve p918](Figure2.png)
+
+![Multinomial Logit](qabazard-state-table3.png)
+![Multinomial Logit](qabazard-state-table4.png)
+
+******
+
+####References
+
+Baum, M. A. 2011. “Red State, Blue State, Flu State: Media Self-Selection and Partisan Gaps in Swine Flu Vaccinations” J Health Polit Policy Law. 36 (6): 1021-1059.
+
+Baumgartner, F. R., and B. D. Jones. 1991. “Agenda Dynamics and Policy Subsystems.” Journal of Politics 53: 1044: 1074.
+
+Bock, R.D. (1972). Estimating item parameters and latent ability when responses are scored in two or more nominal categories. Psychometrika 37, 29–51.
+
+Delli Carpini, Michael X. and Scott Keeter. 1996. What Americans Know about Politics and Why it Matters. Yale University Press.
+
+Jackman, S. 2008. “Measurement.” In The Oxford Handbook of Political Methodology.
+
+Johnson, V. E., and J. H. Albert. 2006. Ordinal Data Modeling. New York, NY: Springer Science & Business Media.
+
+Kaplan, D. 2004. The Sage Handbook of Quantitative Methodology for the Social Sciences. Thousand Oaks, CA: Sage Publications Inc.
+
+Kennedy A., K. Lavail, G Nowak , M Basket, and S. Laundry. 2011. “Confidence about vaccines in the United States: understanding parents' perceptions.” Health Affairs 30 (6): 1151-9.
+
+Lau, R.  R. and D. P. Redlawsk. 2001. “Advantages and Disadvantages of Cognitive Heuristics in Political Decision Making.” American Journal of Political Science 45 (4): 951-971.
+
+Lupia, A. 1994. “Shortcuts versus Encyclopedias: Information and Voting Behavior in California Insurance Reform Elections.” American Political Science Review 88(1): 63-76.
+
+Nyhan, Brendan and Jason Reifler. 2010. “When Corrections Fail: The Persistence of Political Misperceptions.” Political Behavior 32: 303-330.
+
+Treier, S., and D. S. Hillygus. 2009. “The Nature of Political Ideology in the Contemporary Electorate.” Public Opinion Quarterly 73 (4): 679–703.
+
+Salmon D.
+A., L.
+H.
+Moulton, S.
+B.
+Omer, L .
+M.
+Chase, A.
+Klassen, P.
+Talebian, N.
+A.
+Halsey.
+2004.
+“Knowledge, attitudes, and beliefs of school nurses and personnel and associations with nonmedical immunization exemptions.” Pediatrics.
+113 (6): 552-9.
+
+Warshaw, C. 2018. “Latent Constructs in Public Opinion” in The Oxford Handbook of Polling and Survey Methods.
+
+******
+
+####Appendix
+
+![Nominal IRT](appendTABLE1.png)
 
 ## Citations
-Want to cite something?
-
-1. Find your cite key in your bib file.
-1. Put an @ before it, like @Solt2017, or whatever it is
-1. @Solt2017 creates an in-text citation
-1. [@Herndon2014] creates a parenthetical citation
-
-As @Gelman2014 note, the garden of forking paths can pose problems for researchers even when they are acting in good faith.
 
 #Zotero
+
+@mulligan2011
 

### 2019-04-02 paper-template.Rmd
Need to link references to zotero

@@
     template: svm-latex-ms2.tex
-title: "Information, Ideology, and Anti-Vaccination Attitudes" 
+title: "Draft: Information, Ideology, and Anti-Vaccination Attitudes" 
 thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](https://github.com/aq92/7450paper.git).
@@
 @mulligan2011
-
-## Other Common Things
-
-> This will create a block quote, if you want one.
-Dropping a footnote is easy.^[See? Not hard at all.]

### 2019-04-02 paper-template.Rmd
Text

@@
 
-where alpha is the discrimination parameter for a particular item.
-Beta represents the cut point k between each response.
-Theta is the latent trait for a particular person j.
-Graded response models calculate the probability of observing outcome k or ones greater.
-	In nominal response models, the same logic is extended to non-ordered categorical items.
-Nominal models also allow each item to vary in difficulty and parameter.
-The model, proposed by Bock (1972), is helpful because it allows the prediction of each particular response.
-The following equation illustrates the probability of an individual person j selecting a particular category k for each item i.
-
-$$Pr(Y_{ij}= k | \alpha_{i},\beta_{i},\theta) = \frac{exp(\alpha_{ik}\theta_{j}+\beta_{ik})} {\sum_{h=1}^{K} exp(\alpha_{ih}\theta_{j}+\beta_{ih})}$$
-
-#####Model Results and Interpretation:
-
-For the item response models, I drop the respondents that did not answer the questions in Table 1.
-After fitting both a graded response model and a nominal response model, I find that there is evidence for the existence of a meaningful latent trait for three questions.
-The three questions are: (1) How important is it for parents to vaccinate their children?
-(2) Do certain vaccines cause autism in children?
-(3) Do you think vaccines are more dangerous than the disease they are designed to prevent?
-The graded response model yields a non-zero discrimination parameter that is statistically significant for the three questions.
-The nominal response model reports statistically significant differences between responses that are skeptical and not skeptical of vaccines.
-For example, there is a statistically significant difference between the responses that vaccination is “Extremely Important” and “Not Very Important.” The results are included in Table 1 of the appendix.
-
-Beyond the models’ results, Jackman (2008) recommends discussing reliability and validity.
-Regarding reliability, the models report measures of uncertainty that are below conventional measures.
-I argue that the models measured “what they are supposed to be measuring.” Especially in the ordered, graded response model, the distinction between high and lower ordered responses captures a skepticism of vaccination.
-The importance of vaccination and perception of links with autism are both loaded questions that capture the attitudes of individuals towards vaccination.
-Therefore, I am not worried about multidimensionality.
-To test the unidimensionality assumption, I used factor analysis and found that, once accounting for the latent attitude, the questions yield one factor.
-
-                     [Insert Figure 1 & 2 here]
-
-Figures 1 and 2 are characteristic curves that show the role of theta in the probability of observing particular responses.
-Theta is the latent construct or attitude measure.
-For vaccine importance, Figure 1 shows that as theta increases the probability of responding “Extremely Important” decreases.
-When the “Extremely Important” line intersects with the red line, that value of theta yields a higher probability of responding “Very Important.” As theta increases respondents will be more likely to respond, “Somewhat Important.” Finally, a value of theta that continues to increase yields higher probability of responding “Not at all important.”
-
-The role of theta is professing itself more in Figure 2.
-Here, respondents are asked whether certain vaccines cause autism.
-As theta increases the probability of responding “No” decreases.
-As theta increases, we encounter less certain respondents that were “Unsure” if vaccines cause autism.
-When the green line intersects with the blue line, for values of theta greater than 2, respondents are more likely to respond “Yes.”
-
-Taken together, the figures illustrate that the models are measuring what is intended for them to measure.
-As theta increases, the more likely the respondents hold anti-vaccination attitudes.
-In the following section, I predict responses to each of the two questions.
-After looking at predictions of raw responses, I predict theta.
-
-####Multinomial Logit:
-
-In this section I discuss the results of models that directly predict responses.
-As opposed to looking at the theta parameter of the anti-vaccination attitude, I test how the covariates do in predicting raw responses.
-I use both individual and state level covariates in these models.
-After discussing the multinomial model presented, I discuss covariates in both models, and explain the results.
-I show that looking at the latent constructs is necessary because the covariates do not do well at predicting responses.
-
-To test individual level variables, I fit a multinomial logit model to predict individual responses.
-The multinomial model is clustered by state.
-The model tests both the importance of vaccinations and vaccinations and autism responses as the dependent variables.
-In this model, I incorporate state level variables.
-I use a multinomial model instead of an ordered logit.
-Ordered logit models do not allow clustering by state.
-
-#####Independent Variables:
-
-I argue that states that facilitate frequent interaction between citizens and doctors should have less skepticism towards vaccination.
-If citizens get their information from doctors, they should be more likely to have less professed anti-vaccination concerns.
-In order to capture the conditions that facilitate frequent interaction between individuals and doctors, I include several state-level variables.
-State level data is taken from the Kaiser Family Foundation dataset on health care.
-State level variables are from 2014, a year before the survey was conducted.
-The first state-level variable is percent of adults that have not seen a doctor in the past twelve months.
-The second variable is a measure of the percent of uninsured individuals by state.
-
-I also use individual level data that was collected during the survey.
-I use an ideology variable to test competing hypotheses about anti-vaccination sentiments.
-The ideology variable is an ordered variable that ranges from very conservative to very liberal.
-Baum (2011) argues that anti-vaccination opinions are shaped by ideology.
-Although Baum was looking at H1N1 vaccines, there is still reason to believe that the logic applies to the claims made in this article.
-
-#####Controls:
-
-At the individual level, I control for seven variables.
-I control for religiosity to account for variation explained by religious belief.
-States allow exemptions from vaccination for religious reasons.
-Therefore, religious concerns are expected to influence attitudes towards vaccinations.
-The religiosity variable is measured by church attendance.
-I include age to account for a generational differences between respondents.
-The variable is ordinal and is broken into ten year intervals.
-I include education to account for variation in knowledge that results from differences in formal education.
-The variable is ordinal and measures whether respondents completed high school, some college, college, or post graduate degrees.
-There is reason to believe that differences in income may allow more access to reliable information or alternate information.
-Income is measured as monthly household income.
-I include a dichotomous variable that indicates for whether the respondent was a parent.
-I include gender and race to account for demographic and other distinctions between respondents.
-A respondent is a male if the gender variable equals 1.
-Race is measured as a dichotomous variable and equals 1 when the respondent is white.
-
-At the state level I include a control that accounts for the percent of children that are uninsured.
-The control is necessary to separate the state policy implications.
-Children are insured under federal mandates.
-If they are not separate from the percent uninsured variable it would be will be misleading.
-I include an interaction between percent health insurance coverage and individual ideology.
-I include this variable because I use a multilevel modelling in Table 3.
-Therefore, it is included in both models so they are consistent.
-
-                     [Insert Table 2 here]
-
-#####Results:
-
-The results are presented in Table 2.
-The omitted response is the baseline category for each model.
-Model 1 uses the question about the importance of vaccinations as the dependent variable.
-Model 2 uses perception of links to autism as the dependent variable.
-Based on the results, there is no evidence for any of the variables having a consistent effect on vaccine skepticism.
-Consistency would require that variables predict a higher likelihood of finding vaccines not important and expressing worry about links to autism.
-In both models, particular variables may predict a response but not a consistent attitude.
-The results illustrate the limits of looking at direct responses and not using item response models.
-
-                     [Insert Table 3 here]
-
-####Item Response Models:
-
-More meaningful results are observed using item response models.
-In the previous model, I predicted responses to each question.
-Here, I will predict the value of theta, conditional on the covariates.
-I use a mixed linear model and group respondents according to states.
-The dependent variable is the predicted value of theta for each respondent.
-I find no statistically significant relationship between the percent of individuals that have seen doctors and anti-vaccination attitudes.
-I find, all else equal, that higher values of theta are associated with individuals from states with higher uninsured populations.
-Therefore, the results only confirm my second hypothesis.
-
-There seems to be a link between state health care policy and anti-vaccination attitudes.
-I predicted that the link operates through interaction with doctors.
-However, the variable that measures interaction with doctors is not statistically significant.
-Given the controls that are included at the individual-level the results still suggest that there is more evidence for the knowledge deficit theory than ideology.
-The results also indicate that, all else equal, more educated respondents have lower skepticism towards vaccination.
-Also, white respondents are more likely to have higher skepticism.
-Men are less likely to have skepticism towards vaccination.
-However, these results are not theorized in this article.
-
-####Conclusion:
-
-Although anti-vaccination sentiments receive coverage in the news, social scientist have not studied them extensively.
-The medical community agrees that there is no evidence that links childhood vaccination regimens to autism.
-However, politicians and interest groups act based on misconception.
-In this article, I show that anti-vaccinations sentiments are more prevalent in states where individuals have less interaction with medical professionals.
-
-I argue against claims that attribute anti-vaccination sentiments to ideology.
-Beyond the fact that politicians on both sides of the ideological spectrum have raised these concerns, I show that there is no evidence of effects of ideology in the 2015 survey.
-I argue in favor of the knowledge deficit hypothesis.
-My findings expand on work that finds that more reliable sources of information lead to less skepticism towards vaccination.
-
-Future research should begin by gathering more data on anti-vaccination sentiments.
-With individual-level data on interaction with doctors, I could have more evidence to test the link between health policy and anti-vaccination attitudes.
-Also, the effects of measles and mumps outbreaks on public opinion is not clear.
-With more data across different points in time, scholars may be able to identify the effects outbreaks as information shocks.
-
+where alpha is the discrimination parameter for a particular item. Beta represents the cut point k between each response. Theta is the latent tr
 ******
@@
 
-![Nominal IRT](appendTABLE1.png)
-
 ## Citations

### 2019-04-07 qabazard-final.Rmd
Add files via upload

--- 2019-04-02 paper-template.Rmd
@@
 ---
-output: 
-  pdf_document:
-    citation_package: natbib
-    keep_tex: false
-    fig_caption: true
-    latex_engine: pdflatex
-    template: svm-latex-ms2.tex
-title: "Draft: Information, Ideology, and Anti-Vaccination Attitudes" 
-thanks: "The paper's revision history and the materials needed to reproduce its analyses can be found [on Github here](https://github.com/aq92/7450paper.git).
-Corresponding author: [ahmad-qbazard@uiowa.edu](mailto:ahmad-qabazard@uiowa.edu).
-Current version: `r format(Sys.time(), '%B %d, %Y')`."
-author:
-- name: Ahmad S. Qabazard
-  affiliation: University of Iowa
-abstract: "Anti-vaccination attitudes are prevalent among individuals affiliated with both major political parties.
+title: "Information, Ideology, and Anti-Vaccination Attitudes"
+author: "Ahmad Qabazard"
+date: "12/16/2018"
+header-includes:
+    - \usepackage{setspace}\doublespacing
+output: pdf_document
+fontsize: 12pt
+
+---
+
+####Abstract:
+
+Anti-vaccination attitudes are prevalent among individuals affiliated with both major political parties.
 What determines anti-vaccination attitudes?
@@
 I established the necessity of looking at vaccinations as latent constructs by showing the difference in model predictions.
-Using a mixed linear model, I predict values of a latent construct, theta, and the results show relationships that are obscured by looking at direct responses with a multinomial logit."
-keywords: "Vaccination, State Politics"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-fontsize: 12pt
-spacing: single
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
-biblio-style: apsr
-citecolor: black
-linkcolor: black
-endnote: no
----
+Using a mixed linear model, I predict values of a latent construct, theta, and the results show relationships that are obscured by looking at direct responses with a multinomial logit.
 
@@
 ![Nominal IRT](appendTABLE1.png)
-
-## Citations
-
-#Zotero
-
-@mulligan2011
